---
title       : MTCARS Data Visualisation
subtitle    : Course Project for Developing Data Products
author      : Foo Ce Wei
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## MTCARS Dataset
This shiny app uses data from the MTCARS dataset.
```{r}
library(datasets)
head(mtcars)
```

---

## Output
It displays a boxplot of the selected variable against miles per gallon (mpg).
For example, cylinders (cyl) against mpg.

```{r echo=FALSE}
boxplot(mpg~cyl, data = mtcars)
```

---

## Input Variable
You can specify one of the following variables to plot against mpg:
* Cylinders (cyl)
* Transmission (am)
* Gears (gear)
* Carburetors (carb)
* Weight (wt)
* Displacement (disp)
* Horsepower (hp)

---

## Boxplot Colour
You can also specify one of the following colours for the boxplot:
* White
* Blue
* Green
* Red
* Yellow

---

## Have Fun!
The shiny app can be accessed via the following link:
[http://foocewei.shinyapps.io/mtcars](http://foocewei.shinyapps.io/mtcars)
